An Open Repository of Real-Time COVID-19 Indicators

### 2021-06-17 forecast/paper/paper.tex
Fix link, move figs

Lastly, our treatment of the Google-AA signal is different from the rest.
Because Google's team did not start publishing this signal until early
September, 2020, we do not have true vintage data before then.
Furthermore, the latency of the signal was always at least one week
through 2020.  However, this
signal is never revised after initial publication (confirmed via personal
communication with the Google team that produces this signal) and
furthermore the latency of the signal is not an unavoidable property
of the data type, so we simply use finalized values for it in our analysis.

@@

Over the prediction period, all auxiliary indicators are available (in the
proper vintage sense) for all locations and prediction times, except for the
Google-AA signal, which is only observed for an average of 105 (of 306) HRRs.
This is due to the fact that the COVID-19 search trends data is released
after applying differential privacy techniques \cite{Bavadekar:2020}, and a
missing signal value means that the level of noise added in the differential
privacy mechanism is high compared to the underyling search count.  In other
words, values of the Google-AA signal are clearly \textit{not} missing at
random.  It seems most appropriate to impute missing values by zero, and this 
is what we do in our analysis.

@@

Finally, to quantify the importance of training and making predictions using
proper vintage data, we ran a parallel set of forecasting and hotspot prediction 
experiments using finalized data. The results, given in the supplement, show
that training and making predictions on finalized data can result in overly
optimistic estimates of true test-time performance (up to 10\% better in terms
of average WIS or AUC). Furthermore, since indicators can have
greatly different backfill profiles, the use of finalized data in
retrospective evaluations can even change the relative ordering of
methods.  For example, CHNG-CLI and DV-CLI
when trained on finalized data perform very similarly for
the forecasting task.  This makes sense since they are both claims-based indicators measuring supposedly the
same thing.  However, DV-CLI outperforms CHNG-CLI on vintage data,
reflecting its less severe backfill profile.

% TODO note what we said here about the supplement

@@

>>>>

Lastly, our treatment of the Google-AA signal is different from the rest.
Because Google's team did not start publishing this signal until early
September, 2020, we do not have true vintage data before then.  Furthermore, the
latency of the signal was always at least one week through 2020.  However, this
signal is never revised after initial publication (confirmed via personal
communication with the Google team that produces this signal) and furthermore
the latency of the signal is not an unavoidable property of the data type, so we
simply use finalized signal values it, with zero latency, in our analysis.

@@

Over the prediction period, all auxiliary indicators are available (in the
proper vintage sense) for all locations and prediction times, except for the
Google-AA signal, which is only observed for an average of 105 (of 306) HRRs.
Such missingness occurs because the COVID-19 search trends data is
constructed using differential privacy methods \cite{Bavadekar:2020}, and a 
missing signal value means that the level of noise added in the differential
privacy mechanism is high compared to the underyling search count.  In other
words, values of the Google-AA signal are clearly \textit{not} missing at
random.  It seems most appropriate to impute missing values by zero, and this 
is what we do in our analysis.

@@

Finally, to quantify the importance of training and making predictions using
proper vintage data, we ran a parallel set of forecasting and hotspot prediction 
experiments using finalized data. The results, given in the supplement, show
that training and making predictions on finalized data can result in overly
optimistic estimates of true test-time performance (up to 10\% better in terms
of average WIS or AUC). Furthermore, since indicators can have greatly different
backfill profiles, the use of finalized data in retrospective evaluations can
even change the relative ordering of models.  For example, CHNG-CLI and DV-CLI
when trained on finalized data perform very similarly for the forecasting task.
This makes sense since they are both claims-based indicators measuring
supposedly the same thing.  However, DV-CLI outperforms CHNG-CLI on vintage
data, reflecting its has a less severe backfill profile.
% TODO note what we said here about the supplement

@@

Reiterate importance of AS OF

Not the end of the story.  Should we even be forecasting case rates?  More
careful models---combine hotspots and forecasting?

### 2021-06-17 indicators/paper/paper.tex
Fix link, move figs

In what follows, we present examples of the usefulness of some of the novel
signals available in the API. These examples demonstrate that such indicators
are meaningfully related to COVID activity, that they provide alternate views on
pandemic activity that are not subject to the same reporting glitches and delays
as traditional public health surveillance streams, and that they provide
information about public behavior and attitudes that are not available from any
other source. Code to reproduce all examples (which uses the \texttt{covidcast}
R package and fetches data directly from the API) can be found at
\url{https://www.github.com/cmu-delphi/covidcast-pnas/indicators/code/}.

@@

% TODO
% RJT: @AR Note what I claimed we would do above!  I'm thinking we can just
% produce a big batch of case trends over the same time period and for the same
% signals, but for each US state (and territory?), and for the 50 most populous
% counties. AND maybe for this (below national) we should use CLI-in-community
% rather than CLI, from the survey

@@

% TODO 
% RJT: @AR Consider for the supplement.  [Or skip it?  Not all that important 
% but I think it would be nice to do.  Maybe you can delegate this to Logan,
% Aaron, Jingjing, etc.] 
% - Hospitalization trends?
% - Hospitalization correlations?
%  (I see you already have a plot for the first ... but I'm a bit bothered by
%  the fact that the HHS data looks to have such strong weekday effects that we
%  don't attempt to correct for ... perhaps we use do a 7-day rolling avg. Made
%  easy with modeltools)
% If we do so, we should refer to it in the text, this subsection (for time
% trends) and next (for correlations)

>>>>

In what follows, we present examples of the usefulness of some of the novel
signals available in the API. These examples demonstrate that such indicators
are meaningfully related to COVID activity, that they provide alternate views on
pandemic activity that are not subject to the same reporting glitches and delays
as traditional public health surveillance streams, and that they provide
information about public behavior and attitudes that are not available from any
other source. Code to reproduce all examples (which uses the \texttt{covidcast}
R package and fetches data from the API) can be found at
\url{https://github.com/cmu-delphi/covidcast-pnas/tree/main/indicators/code/}.

@@

@@
